### 2020-08-29 thesis/thesis.tex
Extend Freak usage guide

    After compiling and linking program to PATH, one may evaluate program as
    follows: \verb!freak programs/choicesList.fk! The actual code is described in Section~\ref{sec:choice-example}

>>>>

    After compiling and linking program to PATH, one may evaluate program as
    follows: \verb!freak programs/choicesList.fk! The actual code is described
    in Section~\ref{sec:choice-example}:

\begin{verbatim}
Usage: freak [options] [filename]
Options:
                       Evaluate program
   -c, --cps           CPS-translate program
   -h, --help          Print this message and exit
   -p, --parse         Parse program
   -ds, --desugar      Parse and run AST transformations
   -v, --validate      Run available static analysis
\end{verbatim}
